
\section{}




\bigskip

Dear Hiring Manager, 

\bigskip
\bigskip


\hspace{1cm}I am writing to express my interest in the Data Scientist - Geographic Information Systems 1 role with SRP. I am thrilled at the opportunity to apply; my unique background and skill set make me an excellent candidate. I hold a Bachelors of Science in Earth and Space Exploration with an emphasis in Astrophysics, and have professional experience in finance, management, and customer service. My skills in data analysis, project management, and strong communication align well with the role.  \\
\medskip
\hspace{1cm}The rigorous coursework required to achieve a degree in Astrophysics has equipped me with a solid foundation in analytical thinking, data analysis, and problem-solving skills. While pursuing my degree, I branched out and gained experience directly related to a professional career. Participating in a range of systems engineering courses and projects, I gained experience working in team-based projects, simulating professional environments. Outside my degree path, I have taken courses in geology and programming. Specifically, I gained skills in python, data analysis, and in depth understanding of the Arizona landscape. \\
\medskip
\hspace{1cm}I am currently a loan funding processor with Wells Fargo Bank. I coordinate the funding of 5-10 mortgage loans on a daily basis, and I have never missed a deadline or caused a delay in the process. In earlier roles, I worked a range of jobs that helped develop a diverse set of skills. I spent time working as a technician at a bicycle repair shop. I managed orders and created work schedules based on the availability of parts from vendors. During the summers, I managed a water park. This was a high-stress environment where I had to oversee a large team while performing a range of other duties.\\     
\medskip
\hspace{1cm}In my personal life, I am extremely passionate about the outdoors. I spend much of my time using public satellite data to plan hikes and find interesting locations. This role combines my passion for data analysis with my love of maps and geographic data. My unique education and work background will bring diverse viewpoints to the team. Working for SRP would allow me to apply my skills to important, real world problems. \\
\bigskip
Sincerely, \\
\medskip
Nathaniel Rogers
