\section{}




\bigskip

Dear Hiring Manager, 

\bigskip
\bigskip

\hspace{1cm}I am writing to express my strong interest in the Quality Engineer role at The Boeing company. With my background in astrophysics, aerospace project management, and mission design, I am confident in my ability to contribute to the success of the Boeing company. \\
\medskip
\hspace{1cm}My academic background is in astrophysics; I have a Bachelor of Science in Earth and Space Exploration, with an emphasis in Astrophysics from Arizona State University. The rigorous coursework required to achieve a degree in Astrophysics has equipped me with a solid foundation in analytical thinking, data analysis, and problem-solving skills—essential qualities for effective quality engineering. While pursuing my degree, I have been able to branch out and gain experience directly related to a professional career. Participating in SpaceWorks and my senior capstone, offered by the School of Earth and Space Exploration, I gained direct experience working in team-based projects, simulating professional aerospace environments. Outside my degree path, I have taken courses in project management to hone my teamwork skills and gain a deeper understanding of project management theory.\\
\medskip
\hspace{1cm}I have been lucky enough to participate in coursework that directly simulated a professional environment. In the second semester of the SpaceWorks course path, I worked in a semester long project with a team of four people. Through the course of the semester, I designed the mechanical housing of an infrared instrument, I created a unique shutter assembly, and designed the internal structure and system architecture of the instrument. I acted as project manager, creating a schedule and ensuring proper contributions from the group. After the instrument was assembled, I worked with my team to verify the performance of it. The instrument was tested in a vacuum environment, and our data collection was verified to have a thermal accuracy of 2.5 degrees. The project required the team to participate in traditional NASA control gates. We developed a science requirement review, preliminary design review, critical design review, and we presented our findings in an end item data package presentation. \\
\medskip
\hspace{1cm}In addition to the SpaceWorks courses, I have specific experience in model based systems engineering and systems engineering. My senior capstone project was the CAMEO Group. The CAMEO Group sought to investigate the application of CAMEO software in the context of CubeSat missions. The project created a thermal anomaly detection system in the CAMEO model based systems engineering environment. This project lays the foundation for more extensive verification of CubeSat thermal performance before launch; this would increase the success rate of CubeSat missions. This course, on top of "Systems Engineering for Exploration" has given me extensive experience in aerospace project design, management, and functional analysis. \\
\medskip
\hspace{1cm}I have a particular interest in The Boeing Company. Boeing has an unparalleled reputation for aerospace innovation and technological advancement. Boeing's commitment to pushing the boundaries of what is possible in aviation aligns seamlessly with my own passion for exploration and discovery, cultivated through my academic background in astrophysics. I am eager to be a part of a team that embraces challenges, fosters innovation, and continues to redefine the possibilities of flight and space exploration. Boeing's legacy of excellence and its commitment to pushing the boundaries of what is possible in aviation makes it the ideal environment for me to apply my skills and contribute to the cutting-edge advancements in the aerospace industry.\\
\medskip
\hspace{1cm}I am confident that my academic background, coupled with my hands-on experience in aerospace engineering, makes me a strong fit for the Quality Engineer role at The Boeing Company. I would welcome the opportunity to discuss further how my skills and experiences align with your company's needs.\\
\medskip
\hspace{1cm}Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to the success of The Boeing Company.
