%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Wells Fargo Bank}{October 2024 -- Present}
    {Associate Loan Funding Processor}{Chandler, Arizona}
    \resumeItemListStart
        \resumeItem{Support Wells Fargo Home Mortgage by processing and validating mortgage documents and perform multiple moderately complex operational tasks relating to the mortgage closing and funding process.}
        \resumeItem{Oversee the transfer of funds from the lender (Wells Fargo) to escrow companies.}
        \resumeItem{Interact with internal and external clients and collaborate with peers, colleagues and managers to resolve issues and achieve goals.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Mesa Golfland Sunsplash}{March 2018 -- July 2024}
    {Aquatics Manager: Maintenance Safety Officer}{Mesa, Arizona}
    \resumeItemListStart
        \resumeItem{Acted as manager on duty, overseeing staffing of the entire water park, monitored and adjusted pool chemistry, and ensured proper operations of all water park attractions.}
        \resumeItem{Instructed and certified lifeguards to perform at a high level. Lifeguards I certified went on to achieve gold certificates in aquatic safety.}
        \resumeItem{Effective leader overseeing teams of 5-10 lifeguards, ensuring safety of guests and guards at a high level. Maintained standards of vigilance and work efficiency among guards.}
        \resumeItem{Implemented and maintained a database to track audits and safety training, focusing on data entry and implementing remediation plans.}
     %   \resumeItem{Oversaw and managed safety concerns while working on a range of maintenance projects.  }
    \resumeItemListEnd
    
   % \resumeSubheading
   % {Junction Bike Company}{November 2020 -- April 2023}
   % {Service Writer and Technician}{Mesa, Arizona}
   % \resumeItemListStart
      %  \resumeItem{Facilitated migration to a cloud based POS system to track inventory and manage work tickets.}
      %  \resumeItem{Created schedules, ordered materials, and facilitated labor for a range of projects. }
     %   \resumeItem{Developed a range of technical skills including hands on fabrication, engineering, and experience working in a collaborative workshop.}
 %   \resumeItemListEnd

\resumeSubHeadingListEnd