%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{SESE Senior Exploration Capstone} $|$ \emph{CATIA, Cameo Systems Modeler, Model Based Systems Design, MBSE, Python, Jython,  }}    {}
    \resumeItemListStart
        \resumeItem {Examined the applications of MBSE software and methodology in the context of Cubesat missions.}
        \resumeItem{Utilized structure diagrams in the Cameo Systems Modeler to create a thermal model of a Cubesat mission. Defined systems and subsystems in Block Definition Diagrams, ran simulations in Cameo Simulation Toolkit.}
        \resumeItem{Identified potential thermal anomalies using the basic model built. This framework could be used to ensure the success of Cubesat missions before launch.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Space Works II} $|$ \emph{Siemens NX CAD software, Microsoft Projects, Circuits, Python, Arduino}}{}
    \resumeItemListStart
        \resumeItem{Designed and built an infrared instrument that was required to work in space like conditions. Instrument was built around pre-existing sensor, the instrument body, shutter mechanism, and software were custom.}
        \resumeItem{Worked as the project manager and lead design officer. Designed the instrument body, shutter mechanism, and internal structure in Siemens NX. Printed and assembled components.}
        \resumeItem{Completed system captured 30 images of a thermal Target while under 5 torr, temperature of thermal target was measured to be within +- 2.5 degrees accuracy.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Exploration Systems Engineering} $|$ \emph{STM, requirements, systems engineering theory, design fundamentals}}{}
    \resumeItemListStart
        \resumeItem{Worked through the requirements development, trade studies, the project life cycle, system hierarchy, risk analysis, and cost analysis for a proposed space mission.}
        \resumeItem{Successfully developed and presented requirements reviews in the style and context of NASA funded missions.}
    \resumeItemListEnd

\resumeSubHeadingListEnd