\section{}




\bigskip

Dear Hiring Manager, 

\bigskip
\bigskip
   \hspace{1cm} I am writing to express my keen interest in the Model-Based Systems Engineer position at Lockheed Martin. With a background in astrophysics, coupled with hands-on experience in aerospace project management and mission design, I am excited about the opportunity to contribute to the innovative work being done at Lockheed Martin.\\
    \medskip{}
    \hspace{1cm} My academic background is in astrophysics; I have a Bachelor of Science in Earth and Space Exploration, with a emphasis in Astrophysics from Arizona State University. The rigorous coursework required to achieve a degree in Astrophysics has equipped me with a solid foundation in analytical thinking, data analysis, and problem-solving skills—essential qualities for effective systems engineering. Moreover, I've actively sought out opportunities to apply my academic knowledge to real-world scenarios. Engaging in projects such as SpaceWorks and my senior capstone, provided me with invaluable experience in team-based collaboration within simulated professional aerospace environments, and model-based systems engineering in Cameo. Systems Engineering for Exploration gave me direct experience working in a team going through the entire design process for a CubeSat mission. Additionally, I have supplemented my academic pursuits with coursework in project management, further enhancing my teamwork skills, understanding of project management theory, and harboring a passion for agile project approaches. \\
    \medskip{}
    \hspace{1cm} For my senior capstone project, my team investigated the application of model based systems engineering software and methodologies in the context of cubesat missions. My group was provided the thermal telemetry data from the LunaH mapper, a mission flown by ASU. I used CATIA Magic System of Systems Architect to model the structure of the LunaH satellite in SysMl. I built a rough model of the thermal performance of the satellite. We used this thermal model in addition to a thermal anomaly investigate under what conditions thermal anomalies could occur. This project lays the foundation for more extensive verification of CubeSat thermal performance before launch.
    During my time in the SpaceWorks program, I was involved in a semester-long project where I played a pivotal role in designing the mechanical housing and internal structure of an infrared instrument. Assuming the role of project manager, I orchestrated team efforts, established schedules, and ensured adherence to project milestones. The successful assembly and testing of the instrument in a vacuum environment underscored our team's commitment to precision and quality, resulting in a thermal accuracy of 2.5 degrees. These experiences have fortified my proficiency in aerospace project design, management, and functional analysis.\\
    \medskip{}
    \hspace{1cm}My interest in joining Lockheed Martin is based on my love for the aerospace and defense technology sector, as well as my dedication to support undertakings aimed at enhancing national security. The innovation that characterizes Lockheed Martin, especially in advanced systems engineering and state-of-the-art aerospace solutions makes me excited to be associated with this company. I am excited to belong to a team that takes on complicated obstacles and creates new technologies while making a real difference within worldwide defense and safety. One main reason why I am interested in this job is because it offers me the chance to work at the cutting edge of innovation with a firm that values technical excellence and promotes continuous learning.\\
    \medskip{}
    \hspace{1cm}In conclusion, I am confident that my academic background and practical experience make me a strong candidate for the Systems Engineer position at Lockheed Martin. I have real, hands-on experience writing technical requirements, using MBSE programs, and agile systems engineering. I am enthusiastic about the prospect of discussing how my skills and experiences can contribute to the success of your team. Thank you for considering my application. I look forward to the possibility of further discussing how I can contribute to Lockheed Martin's continued success.\\
    \medskip{}
    \bigskip{}
Sincerely,\\
\medskip{}
Nathaniel Rogers
